Figures

### 2019-05-13 figures/07_model-selection.Rmd
More model comparisons

dt        <- readRDS("../data/dt.rds") %>% 
  dplyr::select("lagoslakeid", "hu4_zoneid", "hu12_zoneid", 
                "tp", "hu12_ppt_mean", "hu12_baseflow_mean",
                "maxdepth", "iwsla_ratio", "ag", "row_crop_pct", "corn", 
                "soybeans", "pasture", 
                "phosphorus_fertilizer_use", "nitrogen_fertilizer_use")
names(dt) <- gsub("_", "v", names(dt))
dt        <- dplyr::filter(dt, 
                           !is.na(phosphorusvfertilizervuse), 
                           !is.na(soybeans), 
                           !is.na(corn),
                           !is.na(maxdepth), 
                           !is.na(tp))
dt <- mutate_at(dt, scale, .vars = vars(-lagoslakeid, -hu4vzoneid, -hu12vzoneid))

@@

>>>>

dt        <- readRDS("../data/dt.rds") %>% 
  dplyr::select("lagoslakeid", "hu4_zoneid", "hu12_zoneid", 
                "tp", "tn", "hu12_ppt_mean", "hu12_baseflow_mean",
                "maxdepth", "iwsla_ratio", "ag", "row_crop_pct", "corn", 
                "soybeans", "pasture", 
                "phosphorus_fertilizer_use", "nitrogen_fertilizer_use")
names(dt) <- gsub("_", "v", names(dt))
dt        <- dplyr::filter(dt, 
                           !is.na(phosphorusvfertilizervuse), 
                           !is.na(soybeans), 
                           !is.na(corn),
                           !is.na(maxdepth), 
                           !is.na(tp), 
                           !is.na(tn))
dt <- mutate_at(dt, scale, .vars = vars(-lagoslakeid, -hu4vzoneid, -hu12vzoneid))

@@

# evaulate fixed effects
# ag + {maxdepth, baseflow, iwslavratio}

(model_forms <- list(
  "tp_depth+bf" = bf(tp ~ ag + maxdepth + hu12vbaseflowvmean),
  "tp_depth+iwsla" = bf(tp ~ ag + maxdepth + iwslavratio), 
  "tp_fe" = bf(tp ~ ag + maxdepth + hu12vbaseflowvmean + iwslavratio), 
  "tn_depth+bf" = bf(tn ~ ag + maxdepth + hu12vbaseflowvmean),
  "tn_depth+iwsla" = bf(tn ~ ag + maxdepth + iwslavratio), 
  "tn_fe" = bf(tn ~ ag + maxdepth + hu12vbaseflowvmean + iwslavratio) 
))

fe_brms <- 
  lapply(seq_along(model_forms), function(i) 
    get_if_not_exists(brm_fit, 
                      paste0("../data/mcmc/fe/", names(model_forms)[i]), 
                      formula = model_forms[[i]], 
                      data = dt))

dplyr::bind_rows(
  lapply(fe_brms, function(x) data.frame(brms::bayes_R2(x)))) %>%
  mutate(Model = names(model_forms), 
         Estimate = round(Estimate, 2)) %>%
  dplyr::select(Model, Estimate)

# evaulate spatial random effects
# {fixed effects} + 1/ag, 1/soybeans, 1/corn
(model_forms <- list(
  "tp_ag" = bf(tp ~  maxdepth + hu12vbaseflowvmean +
                   (1 + ag | hu4vzoneid)),
  "tp_soybeans" = bf(tp ~  maxdepth + hu12vbaseflowvmean +
                   (1 + soybeans | hu4vzoneid)),
  "tp_re" = bf(tp ~  maxdepth + hu12vbaseflowvmean +
                   (1 + ag + soybeans | hu4vzoneid))
))

re_brms <- 
  lapply(seq_along(model_forms), function(i) 
    get_if_not_exists(brm_fit, 
                      paste0("../data/mcmc/re/", names(model_forms)[i]), 
                      formula = model_forms[[i]], 
                      data = dt))

dplyr::bind_rows(
  lapply(re_brms, function(x) data.frame(brms::bayes_R2(x)))) %>%
  mutate(Model = names(model_forms), 
         Estimate = round(Estimate, 2)) %>%
  dplyr::select(Model, Estimate)
